\racets: Faceted Execution in Racket

### 2018-07-24 paper/paper.tex
addnig blurb to abstract on lal
abstract tweaks

\begin{abstract}
Faceted Execution (FE) is a linguistic paradigm for dynamic
information flow control. Using faceted execution, secure program data
is represented by \emph{facets}: decision trees that encode how the
data should appear to its owner (represented by a label) versus everyone
else. When labels are allowed to be first-class (i.e., predicates that
decide at runtime which data to reveal), faceted execution enables
\emph{policy-agnostic programming}: a programming style that allows
privacy policies for data to be enforced independently of code that
computes on that data.

To date, implementations of faceted execution are relatively
heavyweight: requiring either changing the language runtime or the
application code (e.g., by using monads). In this paper, we present
\racets: an extension of Racket to faceted execution via macros. Given
Racket's highly-expressive macro system, our implementation follows
relatively directly from the semantics of faceted execution. To
demonstrate how \racets can be used for policy-agnostic programming,
we use it to build a web-based game of Battleship. Our implementation
sheds light on several interesting issues in interacting with code
written without faceted execution. \racets is currently available
under an open-source license on GitHub.

\end{abstract}

>>>>

\begin{abstract}
Faceted Execution is a linguistic paradigm for dynamic
information-flow control. Under faceted execution, secure program data
is represented by \emph{faceted} values: decision trees that encode how the
data should appear to its owner (represented by a label) versus everyone
else. When labels are allowed to be first-class (i.e., predicates that
decide at runtime which data to reveal), faceted execution enables
\emph{policy-agnostic programming}: a programming style that allows
privacy policies for data to be enforced independently of code that
computes on that data.

To date, implementations of faceted execution are relatively
heavyweight: requiring either changing the language runtime or the
application code (e.g., by using monads). In this paper, we present
\racets: an extension of Racket to faceted execution a library of
macros. Given Racket's highly-expressive macro system, our
implementation follows relatively directly from the semantics of
faceted execution. To demonstrate how \racets can be used for
policy-agnostic programming, we use it to build a web-based game of
Battleship. Our implementation sheds light on several interesting
issues in interacting with code written without faceted execution. Our
\racets implementation is open source, under development, and
available online.
\end{abstract}
